%++++++++++++++++++++++++++++++++++++++++
% Don't modify this section unless you know what you're doing!
\documentclass[letterpaper,12pt]{article}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}
%++++++++++++++++++++++++++++++++++++++++


\begin{document}

\title{Specialization Project}
\author{Aakash S. Mallik, Prof. Di Wu, Prof. Yushan Pan}
\date{\today}
\maketitle

% \begin{abstract}
% The following proposal describes the 
% \textbf{Specialization Project (IE505718)} structure that would be required for the topic \textbf{Affordance Learning for Interaction Design}.
% \end{abstract}


\section{Course code and Name}

IE505718 Specialization Project

\section{Topic}

Affordance Learning for Robotics Interaction Design 

\section{Course content}

\begin{enumerate}
    \item Robotic Design
        \begin{enumerate}
    		\item Basic Concepts in Robotic design.
    		\item Key features in Robotic design. 
    	\end{enumerate}
    \item Robotic Interaction
        \begin{enumerate}
    		\item Basic Concepts in Robotic interaction.
    		\item Key design features in Robotic affordance. 
    	\end{enumerate}  
    \item Affordance Analysis
        \begin{enumerate}
    		\item Affordance classfications.
    		\item Affordance analysis methods. 
    	\end{enumerate}
    \item Simulation Design Platform Development
    	\begin{enumerate}
    		\item An overview of different simulation software
    		\item Detailed analysis of Nvidia Isaac Sim
    	\end{enumerate}
\end{enumerate}

\section{Learning outcome}

\begin{enumerate}
	\item Knowledge
	\begin{enumerate}
		\item To understand the basic knowledge about robotic design.
		\item To overview the robotic affordance analysis methods
		\item To compare different simulation platform for affordance interaction robotic design. 
        \item To explore algorithmic changes needed to incorporate existing Reinforcement Learning implementations in related simulation platform.
	\end{enumerate}
	\item Skill
	\begin{enumerate}
		\item To master Nvidia Isaac Sim platform for robot interaction design.
		\item To implement an application case for robot interaction affordance design in Nvidia Isaac Sim platform. 
        \item To optimize the design process using Reinforcement learning methods.
  
	\end{enumerate}
	\item General Competence
	\begin{enumerate}
		\item Ability to communicate affordance theory and deep learning concepts and main challenges in the robotic design areas.
	\end{enumerate}
\end{enumerate}

\section{Evaluation}

\begin{enumerate}
	\item A working prototype of affordance learning sandbox with documentation
\end{enumerate}

\section{References}

\begin{enumerate}
	\item Learning To Walk in Minutes by Rudin et al and Nvidia.
	\item Graphics and Simulation Courses by Nvidia
\end{enumerate}

\end{document}
